Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex

        \subsubsection{Death} The death stage represents the challenges and adversities
        that life presents. This process evaluates the individual resistance to survive
        in the environment. The better fitness the individual has will increase its
        chances of survival. As time progresses, the demands of nature will also
        increase, pushing for only the best individuals to survive.

>>>>

        \subsubsection{Death} Death is the last step of the animal life cycle,
        as in our algorithm. We chose death as a representation of all the
        environmental challenges for survival, where its execution enforces the
        survival of the fittest. As time progresses, so does increase nature's
        level of danger. The better the individual fitness will increase its
        chances of survival.
